Causal Compatibility Inequalities Admitting of Quantum Violations in the Triangle Scenario

### 2016-11-21 documents/BrazilSlides/slides.tex
Added inequalities for talk

\begin{frame}[shrink=60]
    \frametitle{Party Symmetric Inequality}
    \input{../../figures/inequalities/MosekCertFritzSym_ineq_print}
\end{frame}

@@

@@

>>>>

\begin{frame}[shrink=64]
    \frametitle{Certificate for Fritz Distribution (Full)}
    \begin{center}
        \input{../../figures/inequalities/nosymwitness_ineq_print}
    \end{center}
\end{frame}

\begin{frame}
    \frametitle{Party Symmetric Inequality}
    \input{../../figures/inequalities/MosekCertFritzSym_ineq_print_pretty}
    \vfill
    \textbf{Note:} $\bs{\prob[][113]\prob[][330]}_3$ shorthand sum over permutations:
    \[ \prob[][113]\prob[][330] + \prob[][131]\prob[][303] + \prob[][311]\prob[][033] \]
\end{frame}

\begin{frame}[shrink=60]
    \frametitle{Party Symmetric Inequality (Full)}
    \input{../../figures/inequalities/MosekCertFritzSym_ineq_print}
\end{frame}

@@

\begin{frame}
    \frametitle{Maximal Violation}
    \includegraphics[width=\linewidth]{../../figures/distributions/plotted_dist_I_2_max_violation.pdf}
    \[ \text{Relative Violation:} \qquad V_F = \f{\min_P\bc{I\br{P}}}{I\br{P_F}} \]
\end{frame}

@@

\begin{frame}
    \frametitle{Symmetrized Fritz [Optional]}
    \begin{center}
        \includegraphics[width=\linewidth]{../../figures/distributions/symmetrized_fritz.pdf}
    \end{center}
    \begin{itemize}
        \item More non-local yet not quantum-accessible
        \item Quantum-accessible distributions form non-context set
    \end{itemize}
\end{frame}
